In mathematics, the convolution operation is denoted by $*$ and the convolution $s$ (itself a function) of two functions $k$ and $m$ is defined as

\startplaceformula[reference=cont-conv]
\startformula
s(t) = (k * m)(t) = \int_{{-}\infty}^{{+}\infty} k(x) \cdot m(t-x) \, {\rm d}x
\stopformula
\stopplaceformula
\startplaceformula[reference=disc-conv]
\startformula
s(\color[red]{x}) = (k * m)(\color[red]{x}) = \sum_{\color[blue]{x'} = {-}\infty}^{{+}\infty} k(\color[blue]{x'}) \cdot m(\color[red]{x}-\color[blue]{x'})
\stopformula
\stopplaceformula

For continuous (eq.~\in[cont-conv]) and discrete (eq.~\in[disc-conv]) functions respectivly.
On a computer, we are in practice always working with discrete convolutions so for us the convolution of interest is equation~\in[disc-conv].
If we make the functions $k$ and $m$ two dimentional---they take two arguments as their input---their convolution also becomes two dimentional.

\startplaceformula[reference=twodim-disc-conv]
\startformula
s(\color[red]{x}, \color[red]{y}) = (k * m)(\color[red]{x}, \color[red]{y}) =
\sum_{\color[blue]{y'} = {-}\infty}^{{+}\infty}
\sum_{\color[blue]{x'} = {-}\infty}^{{+}\infty}
k(\color[blue]{x'}, \color[blue]{y'}) \cdot m(\color[red]{x}-\color[blue]{x'}, \color[red]{y} - \color[blue]{y'})
\stopformula
\stopplaceformula

\indentation
Let us known say that $k$ and $m$ are two functions which each index an array of two dimentions.
Meaning that the functions take two indexes as their input arguments.
Let us further assume that $k$ and $m$'s arrays are zero at any index but for those contained in a small area.
For $k$ that area is $[0 \, .. \, \eta_x(k)] \times [0 \, .. \, \eta_y(k)]$ and for $m$ it is $[0 \, .. \, \eta_x(m)] \times [0 \, .. \, \eta_y(m)]$.
In this case, the convolution of $k$ and $m$ reduces to

\startplaceformula[reference=twodim-disc-conv-finite]
\startformula
s(\color[red]{x}, \color[red]{y}) = (k * m)(\color[red]{x}, \color[red]{y}) = 
\sum_{\color[blue]{y'} = 0}^{\eta_y(k)} 
\sum_{\color[blue]{x'} = 0}^{\eta_x(k)} 
k(\color[blue]{x'}, \color[blue]{y'}) \cdot m(\color[red]{x}-\color[blue]{x'}, \color[red]{y} - \color[blue]{y'})
\stopformula
\stopplaceformula

Where $\color[red]{x} \in [0 \, .. \, \eta_x(m)]$ and $\color[red]{y} \in [0 \, .. \, \eta_y(m)]$.

We can already see that equation~\in[twodim-disc-conv-finite] resembles the \quote{green} sum in equation~\in[cv:forward:neuron].
But there is a subtle difference.
In equation~\in[twodim-disc-conv-finite] that indices are subtracted from one another while in equation~\in[twodim-disc-conv-finite] we add them together.
The effect of subtracting instead of adding renders the convolution operation $(*)$ commutative.

\startplaceformula[reference=conv-commute]
\startformula
\startmathalignment
\NC (k * m)(\color[red]{x}, \color[red]{y}) \NC = (m * k)(\color[blue]{x}, \color[blue]{y}) \NR
\NC \sum_{\color[blue]{x}}^{} \sum_{\color[blue]{y}}^{} k(\color[blue]{x}, \color[blue]{y}) \cdot m(\color[red]{x}-\color[blue]{x}, \color[red]{y} - \color[blue]{y}) \NC
= \sum_{\color[red]{x}}^{} \sum_{\color[red]{y}}^{} m(\color[red]{x}, \color[red]{y}) \cdot k(\color[blue]{x}-\color[red]{x}, \color[blue]{y} - \color[red]{y}) \NR
\stopmathalignment
\stopformula
\stopplaceformula

\indentation
So what is the effect of replacing the pluses in equation~\in[cv:forward:neuron] with minuses?
Well at first glance it seems that you cannot do it as you would end up with indexes that are out of bounds for the input image $M$.
But let us assume that $M$ behaves as $m$ meaning that it is zero everywhere where the indices are out of bounds.
What you find if you visualize the computation of $z$ using equation~\in[twodim-disc-conv-finite], is that it is effectivly the same as using equation~\in[cv:forward:neuron] with the kernel flipped about its horisontal and vertical axes.
Which in turn means that flipping the kernel relative to the input, renders the computation of the feature map commutative.

But this is a property that is usefull in mathematical contexts and less so for computing neural networks.
It is equation~\in[cv:forward:neuron] that is commonly used in macine learning applications and the associated mathematical operations is actually what is called the {\em cross-correlation}.
Despite this, neural networks that implement these kinds of neurons are called convolutional even if the underlying mathematical operations is more often than not a close relative of the proper convolution operation.
